\pkg{RProtoBuf}: Efficient Cross-Language Data Serialization in R

### 2014-01-12 papers/jss/article.Rnw
tiny changes
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@759 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

The \texttt{RProtoBuf} package combines a dispatch mechanism 
of the form \verb|method(object, arguments)| (common to R) and the more
traditional object oriented notation \verb|object$method(arguments)|.
Additionally, \texttt{RProtoBuf} implements the \texttt{.DollarNames} S3 generic function
(defined in the \texttt{utils} package) for all classes to enable tab
completion.  Completion possibilities include pseudo-method names for all
classes, plus dynamic dispatch on names or types specific to a given object.

@@

R booleans can accept three values: \texttt{TRUE}, \texttt{FALSE}, and
\texttt{NA}.  However, most other languages, including the Protocol
Buffer schema, only accept \texttt{TRUE} or \texttt{FALSE}.  This means
that we simply can not store R logical vectors that include all three
possible values as booleans.  The library will refuse to store
\texttt{NA}s in protocol buffer boolean fields, and users must instead
choose another type (such as integers) capable of storing three
distinct values.

>>>>

The \texttt{RProtoBuf} package combines a functional dispatch mechanism 
of the form \verb|method(object, arguments)| (common to R) and the more
traditional object oriented notation \verb|object$method(arguments)|.
Additionally, \texttt{RProtoBuf} implements the \texttt{.DollarNames} S3 generic function
(defined in the \texttt{utils} package) for all classes to enable tab
completion.  Completion possibilities include pseudo-method names for all
classes, plus dynamic dispatch on names or types specific to a given object.

@@

R booleans can accept three values: \texttt{TRUE}, \texttt{FALSE}, and
\texttt{NA}.  However, most other languages, including the Protocol
Buffer schema, only accept \texttt{TRUE} or \texttt{FALSE}.  This means
that we simply can not store R logical vectors that include all three
possible values as booleans.  The library will refuse to store
\texttt{NA}s in protocol buffer boolean fields, and users must instead
choose another type (such as enum or integer) capable of storing three
distinct values.
